|

### 2019-09-02 paper.Rmd
Examples added

# Examples
XXX choose 6

## Geometric shapes
### Hollow sphere
We sample points on the surface of a sphere with radius $r=1$ in $p=3$ and $p=5$ dimensions. Using the `geozoo` package [@geozoo], we draw 2000 (5000) points that are uniformly distributed on the surface of a 3d (5d) sphere.
For both examples we start by slicing through the origin with the default parameters, in particular $\epsilon = 0.001$, i.e. $h = 0.1$ in 3d and $h = 0.25$ in 5d. Slicing through the origin results in sections where the points inside the slice are approximately on a circle with the full radius, and each view is similar to that shown in Figure~\ref{fig:renderFunction}. The animated gifs are available at XXX.

@@

### Other geometric shapes

Examples: 4d cube, 4d torus

>>>>

# Examples
## Geometric shapes
### Hollow sphere
We sample points on the surface of a sphere with radius $r=1$ in $p=3$ and $p=5$ dimensions. Using the `geozoo` package [@geozoo], we draw 2000 (5000) points that are uniformly distributed on the surface of a 3d (5d) sphere.
For both examples we start by slicing through the origin with the default parameters, in particular $\epsilon = 0.001$, i.e. $h = 0.1$ in 3d and $h = 0.25$ in 5d. Slicing through the origin results in sections where the points inside the slice are approximately on a circle with the full radius, and each view is similar to that shown in Figure~\ref{fig:renderFunction}. The animated gifs are available at XXX.

@@

### Other geometric shapes
To better understand the slice tour we look at different examples of geometric shapes, see Figure \ref{fig:geoms}. For each shape two selected views are shown. The first column shows views from the slice tour on a 3d Roman surface. The second column shows slices through a 4d torus, revealing different aspects of the shape. The last column shows a 6d cube, where the upper plot shows a view along two of the parameter combinations, allowing to clearly identify the rectangular shape. The panel below shows that this is not typically the case when looking at a randomly selected slice.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.2\textwidth]{gifs/png/roman-surface-centered-010.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/torus-4-centered-015.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/cube-6-centered-001.png}}
\centerline{
\includegraphics[width=0.2\textwidth]{gifs/png/roman-surface-centered-032.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/torus-4-centered-033.png}
\hspace{5mm}
\includegraphics[width=0.2\textwidth]{gifs/png/cube-6-centered-063.png}
}
\caption{Different slices through a Roman surface (left), 4d torus (middle) and a 6d cube (right).}
\label{fig:geoms}
\end{figure*}
